### 2023-04-12 article.tex
Add suggestion, thanks Isto

There exists no standard definition of paradata (\cite{nicolaas2011survey,skold2022interrogating,huvila2022improving}).
Without declaring it a formal definition, however,
paradata is 'data about processes' (and example survey paradata 
are call records and audit trails) \cite{nicolaas2011survey},
or 'data about the data collection process' (\cite{choumert2019using}).
This paper uses the latter as a working definition.

>>>>

There exists no standard definition of paradata (\cite{nicolaas2011survey,skold2022interrogating,huvila2022improving}).
Without declaring it a formal definition, however,
paradata can be understood in general sense as 'data about processes’ (with e.g. survey paradata
termed alternatively as records and audit trails) \cite{nicolaas2011survey},
or in more specific sense in relation to data collection, as 'data about the data collection process' (\cite{choumert2019using}).
This paper uses the latter as a working definition.
